Red Oak: Something Something Algorithmic Policy

### 2015-05-05 draft.tex
..

@@

\begin{document}
\quad \\
\quad \\
\quad \\
\centerline{ \large{Red Oak: Something Something Algorithmic Policy}}
\vspace{1pt}\\
\centerline{Ryan Beckett and Olivier Savary B\'{e}langer} \\
\\
\centerline{April 15, 2015} \\

>>>>

\title{Red Oak: Something Something Algorithmic Policy}
 \authorinfo{Ryan Beckett}{Princeton University}{rbeckett@princeton.edu}
 \authorinfo{Olivier Savary B\'{e}langer}{Princeton University}{olivierb@princeton.edu}

@@

\begin{document}
\maketitle
